Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
edit

A common assumption in observational models of the MW DM halo is that
its minor axis is perfectly aligned with the stellar disc minor axis.
Although it is a reasonable assumption to guarantee the stability of
the galactic disc in simplified models of isolated galaxies, this
might not hold in an explicit cosmological context. 
To examine the degree of validity of this assumption we study in this
section the alignment between the eigenvectors of the inertia tensor of
stellar particles within $0.1R_{200}$ ($\sim 23\pm 2$ kpc) and the
eigenvectors of the dark matter halo shape.
All the measurements are done at $z=0$.

>>>>

A common assumption in dynamical models of the MW DM halo is that
its minor axis is perfectly aligned with the stellar disc minor axis.
Although it is a reasonable assumption to guarantee the stability of
the galactic disc in simplified models of isolated galaxies, this
might not perfectly hold in an explicit cosmological context. 
To examine the degree of validity of this assumption we study in this
subsection the alignment between the eigenvectors of the inertia tensor of
stellar particles within $0.1R_{200}$ ($\sim 23\pm 2$ kpc) and the
eigenvectors of the dark matter halo shape.
